Reproducibility in Plant Pathology

### 2022-04-25 README.rmd
Reknit README after updating text to reflect package structure

This repository is organized as an R package. There are custom R functions, 
`table_of_journals()` and `workflow_dia()` that are used in this repository, along with a bibliography file of the articles that were examined and the notes that are located in `inst/extdata` directory.
We have used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing and for file organisation.

@@

<https://adamhsparks.com/>

>>>>

This repository is organized as an R package.
There is one R function, `import_notes()` that is used in the paper's figure and table making when the file, `analysis/paper/paper.Rmd` is knit.
Additionally, a bibliography file, "references.bib", of the articles that were examined and the notes from the evaluation, "Reproducibility_in_plant_pathology_notes.ods" of the articles are both located in `inst/extdata` directory.
We have used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing and for file organisation.

@@

<https://adamhsparks.netlify.app>
